method

### 2021-10-05 06_Paper/ER-ED/method.Rmd
Update method.Rmd
added comment
added text
added ERQ

@@

>>>>

[...] <!-- Anne tried to implement a sentence here. -->

@@

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contains a number of questionnaires.
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
